% Created 2025-01-06 Mon 18:37
% Intended LaTeX compiler: pdflatex
\documentclass[letterpaper]{book}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath, amsthm, amssymb, amsfonts, amssymb, amscd}
\usepackage[table, xcdraw]{xcolor}
%\usepackage{mdsymbol}
\usepackage{tikz-cd}
\usepackage{float}
\usepackage[spanish, activeacute, ]{babel}
\usepackage{color}
\usepackage{transparent}
\graphicspath{{./figs/}}
\usepackage{afterpage}
\usepackage{array}
\usepackage{pst-node}
\usepackage{imakeidx}
\usepackage{braket}

\usepackage{subfiles} % Best loaded last in the preamble



\newcommand{\ind}{\perp\!\!\!\!\perp}
\newtheorem{teorema}{Teorema}[section]
\newtheorem{prop}[teorema]{Proposici\'on}
\newtheorem{cor}[teorema]{Corolario}
\newtheorem{lema}[teorema]{Lema}
\newtheorem{def.}{Definici\'on}[section]
\newtheorem{afir}{Afirmaci\'on}
\newtheorem{conjetura}{Conjetura}
\renewcommand{\figurename}{Figura}

\newcommand{\zah}{\ensuremath{ \mathbb Z }}
\newcommand{\rac}{\ensuremath{ \mathbb Q }}
\newcommand{\nat}{\ensuremath{ \mathbb N }}
\newcommand{\prob}{\textbf{P}}
\newcommand{\esp}{\mathbb E}
\newcommand{\exe}{{\noindent \sc \textbf{Ejercicio. }}}
\newcommand{\eje}{{\noindent \sc \textbf{Ejemplo. }}}
\newcommand{\obs}{{\noindent \sc \textbf{Observación. }}}
\newcommand{\sol}{{\noindent \sc \textbf{Solución. }}}
\newcommand{\dem}{{\noindent \sc \textbf{Demostraci\'on. }}}
\newcommand{\QED}{\ensuremath{\hspace*{0em plus 1fill}\blacksquare}}

\newcommand{\bg}{\ensuremath{\overline \Gamma}}
\newcommand{\ga}{\ensuremath{\gamma}}
\newcommand{\fb}{\ensuremath{\overline F}}
\newcommand{\la}{\ensuremath{\Lambda}}
\newcommand{\om}{\ensuremath{\Omega}}
\newcommand{\sig}{\ensuremath{\Sigma}}
\newcommand{\bt}{\ensuremath{\overline T}}
\newcommand{\li}{\ensuremath{\mathbb{L}}}
\newcommand{\ord}{\ensuremath{\mathbb{O}}}
\newcommand{\bs}{\ensuremath{\mathbb{S}^1}}
\newcommand{\co}{\ensuremath{\mathbb C }}
\newcommand{\con}{\ensuremath{\mathbb{C}^n}}
\newcommand{\cp}{\ensuremath{\mathbb{CP}}}
\newcommand{\rp}{\ensuremath{\mathbb{RP}}}
\newcommand{\re}{\ensuremath{\mathbb R }}
\newcommand{\hc}{\ensuremath{\widehat{\mathbb C} }}
\newcommand{\pslz}{\ensuremath{\mathrm{PSL}(2,\mathbb Z) }}
\newcommand{\pslr}{\ensuremath{\mathrm{PSL}(2,\mathbb R) }}
\newcommand{\pslc}{\ensuremath{\mathrm{PSL}(2,\mathbb C) }}
\newcommand{\hd}{\ensuremath{\mathbb H^2}}
\newcommand{\slz}{\ensuremath{\mathrm{SL}(2,\mathbb Z) }}
\newcommand{\slr}{\ensuremath{\mathrm{SL}(2,\mathbb R) }}
\newcommand{\slc}{\ensuremath{\mathrm{SL}(2,\mathbb C) }}
\newcommand{\mdlr}{\ensuremath{\mathrm{M}}}
\author{Carlos Eduardo Martínez Aguilar}
\date{\today}
\title{Notas de MAF}
\hypersetup{
 pdfauthor={Carlos Eduardo Martínez Aguilar},
 pdftitle={Notas de Matemáticas Avanzadas para la Física},
 pdfkeywords={},
 pdfsubject={},
 pdflang={Esp}}

\makeindex
\begin{document}

\maketitle
\tableofcontents
\subfile{Capitulo1}
\subfile{Capitulo2}
\subfile{Capitulo3}
\subfile{Capitulo4}

\begin{thebibliography}{9}

\bibitem{Wein} H.F. Weinberger ``A First Course In Partial Differential Equations With Complex Variables and Transform Methods'', Dover Books On Mathematics, New York.
\bibitem{Lebedev} N.N. Lebedev ``Special Functions \& Their Applications'', Dover Books On Mathematics, New York.
\bibitem{Afken} Arfken, George B. et all, ``Mathematical Methods for Physicist, A Comprehensive Guide.'', Ed. Elsevier, Seventh Edition.
\bibitem{Appfel} Appfel, Walter, ``Mathematics for Physics \& Physicists.'', Ed. Princeton University Press, 2007.
\bibitem{Churchill} Churchill R. V. and Brown J. W., ``Fourier Series and Boundary Value Problems'', Ed McGraw-Hill.
\bibitem{Cour-Hil} Courant R and D. Hilbert, ``Methods of Mathematical Physics.'', vol. 1 y 2.
\bibitem{Tijoniv} Tijonov A, ``Ecuaciones de la Física Matemática'', Ed. MIR Moscu, Segunda edición, 1980.
\bibitem{Vladimiriv} Vladimirov V. S. , ``Equations of Mathematical Physics'', Ed. URSS Moscow, 1996.
\bibitem{Kreyszig} E. Kreyszig ``Introductory Functional Analysis With Applications'', John Wily \& Sons.

\end{thebibliography}

\end{document}
